%----------------------------------------------------------------------------------------------------------------------%
%	Employment History Section Title
%----------------------------------------------------------------------------------------------------------------------%
%BEGIN_FOLD

	% Display header for the employment history section
	\CVSection{Employment History}% 

%END_FOLD
%----------------------------------------------------------------------------------------------------------------------%
%	Employment History Section Content
%----------------------------------------------------------------------------------------------------------------------%
%BEGIN_FOLD

	\begin{EmploymentHistoryEntries}%
		\EmploymentHistoryEntry{Software Engineer - Full Stack}%
		{Jan 2030}{Present}%
		{Lloyds Banking Group, Wellington Place, Leeds LS1 4AP}%
		{https://www.lloydsbank.com/}%
		{
			\item Work with the full stack team to redesign and re-release the companies mobile banking application.
			\item Collaborate with a team of full stack software engineers to design, develop, and integrate efficient solutions.
			\item Rewrite the the authentication back-end to reduce server stress, and decrease end-user logon issues.
			\item Work with the existing DevOps pipeline to produce deliverables on time.
		}%
		\EmploymentHistoryEntry{Software Engineer/Web Developer}%
		{Aug 2028}{Jan 2030}%
		{Self Employed Contractor}%
		{https://www.skyebreach.com}%
		{
			\item Communicate and organise client projects through the use of agile methodologies and software.
			\item Design interesting and useful front-end UI for clients in both Figma and Penpot.
			\item Implement full stack systems using a wide array of web frameworks.
			\item Deploy custom built websites and web-apps using both traditional and cloud methodologies.
			\item Design back-ends to effectively support decoupled front-end applications.
		}%
	\end{EmploymentHistoryEntries}%

%END_FOLD
%----------------------------------------------------------------------------------------------------------------------%